Puck Predictions: Unraveling the NHL Game Forecasting Riddle

### 2024-04-12 Latex/draft.tex
Moved algorithm 1 to the appendix (save space).

To simulate a game, we performed this Monte Carlo Algorithm (see Algorithm~\ref{alg:monte_carlo_algorithm}) that acted like a random walk through the Markov Chain (Note that the {\tt KDE\_times()} is a KDE model fit on the amount of seconds that transpired between 
each hockey event for all NHL games over the course of 13 years).
\begin{algorithm}
    \caption{Simulation Algorithm}
    \begin{algorithmic}[1]
        \State $\text{time\_remaining} \gets 3600$
        \Comment{NHL games are 3600 seconds}
        \State $s_0 \gets "\#"$
        \Comment{The "\#" symbol represents the start of a game}
        \State $s_1 \gets "\#"$
        \State $s_2 \gets "\#"$
        \State $\text{event\_counts} \gets \text{dictionary()}$

@@

>>>>

To simulate a game, we performed this Monte Carlo Algorithm (see Algorithm~\ref{alg:monte_carlo_algorithm} in Appendix~\ref{mcmc_app}) that acted like a random walk through the Markov Chain (Note that the {\tt KDE\_times()} is a KDE model fit on the amount of seconds that transpired between 
each hockey event for all NHL games over the course of 13 years).
% \begin{algorithm}
%     \caption{Simulation Algorithm}
%     \begin{algorithmic}[1]
%         \State $\text{time\_remaining} \gets 3600$
%         \Comment{NHL games are 3600 seconds}
%         \State $s_0 \gets "\#"$
%         \Comment{The "\#" symbol represents the start of a game}
%         \State $s_1 \gets "\#"$
%         \State $s_2 \gets "\#"$
%         \State $\text{event\_counts} \gets \text{dictionary()}$

%         \While{$\text{time\_remaining} > 0$}
%             \State $\text{next\_state} \gets \text{sample from } \text{MC(curr\_state)}$
%             \State $\text{event\_counts}[\text{next\_state}] \mathrel{+}= 1$

%             \State $s_0 \gets s_1$
%             \State $s_1 \gets s_2$
%             \State $s_2 \gets \text{next\_state}$

%             \State $\text{event\_time} \gets \text{sample from } \text{KDE\_times()}$
%             \State $\text{time\_remaining} \gets (\text{time\_remaining} - \text{event\_time})$
%         \EndWhile
%     \end{algorithmic}
%     \label{alg:monte_carlo_algorithm}
% \end{algorithm}

@@

\newpage

\section*{Appendix}

\appendix
\section{MCMC Sampling Algorithm}
\label{mcmc_app}

\begin{algorithm}
    \caption{Simulation Algorithm}
    \begin{algorithmic}[1]
        \State $\text{time\_remaining} \gets 3600$
        \Comment{NHL games are 3600 seconds}
        \State $s_0 \gets "\#"$
        \Comment{The "\#" symbol represents the start of a game}
        \State $s_1 \gets "\#"$
        \State $s_2 \gets "\#"$
        \State $\text{event\_counts} \gets \text{dictionary()}$
